On Sample Size for Block Bootstrap Confidence Intervals to Have Desired Coverage Rates

### 2023-06-01 Manuscript/manuscript.tex
minor; removed resolved

The necessary sample size for bootstrap standard errors to provide valid
uncertainty measures in practice has not been extensively studied. For
independent data and non-block bootstrap, \citet{hesterberg2015teachers} notes
that while percentile-based CIs from nonparametric bootstrap
are more accurate than $t$-intervals for larger sample sizes, they are
less accurate for smaller sample sizes. \citet{chernick2009revisiting} finds that the
the best choice of method for estimating
the parameter of a distribution is dependent on the sample size, the number of
bootstrap resamples, and the confidence level. In the context of structural equation
modeling, \citet{nevitt2001performance} find
that a sample size of 200--1000 is usually sufficient for interval estimation
using standard nonparametric bootstrap. For dependent data, the necessary
sample
size for bootstrap is even less clear. In the setting of linear regression with a
focus on estimating the proportion of 
variation attributable to a certain variable, \citet{burch2012nonparametric} finds
that three nonparametric bootstrap methods (Standard, Percentile, and Bias-Corrected
and
Accelerated) approach the coverage of a pivotal quantity as $n$ gets larger for an
underlying normal distribution. However, they find that for other distributions, 
coverage may deteriorate as $n$ increases. 
When attempting to create interval estimations for the Pearson correlation 
coefficient of bivariate normal data, \citet{puth2015variety} find bootstrap 
methods to be less accurate than the Fisher's transformation method even 
for a sample of size $n = 100$ and correlation coefficient equivalent to 0.
Few studies have provided a practical guide on what size is needed
for block bootstrap inference for dependent data.
In a linear regression setting
with
dependent data where the
regression errors are generated from a homoscedastic AR(1) process, 
\citet{goncalves2005bootstrap} find that standard error
estimates from moving 
block bootstrap in small samples may be more accurate than
inference from closed-form asymptotic estimates, but moving block bootstrap 
\jy{did they do block or standard bootstrap?}
\mc{moving block bootstrap}
CIs still do not have sufficient coverage of the target parameter even for sample size
$n = 1024$.
\jy{I added more references to the reference folder that studied coverage of
  bootstrap CIs but not block bootstrap CIs.}

@@

\paragraph{Standard Normal CI}
Assuming that $\hat\theta_n$ is asymptotically normally distributed with
$\theta$ as the mean, we just need an estimate of the standard error to
construct an approximate CI \citep[p.168]{efron1993introduction}.
Let $\widehat{\text{SE}}$ be the empirical standard error of the block bootstrap
copies of $\hat\theta_n^{(b)}$, $b = 1, \ldots, B$.
A $(1 - \alpha)$ standard normal CI is
\[
(\hat{\theta}_{n} - z_{(1-\alpha/2)}\widehat{\text{SE}}, \quad
\hat{\theta}_{n} - z_{(\alpha/2)}\widehat{\text{SE}}).
\]
This CI is centered by the point estimator $\hat\theta_n$ and is symmetric.
Its validity relies on whether the distribution of $\hat\theta_n$ is reasonably
well approximated by its asymptotic normal distribution and whether the
bootstrap $\widehat{\text{SE}}$ approximates the true standard error.

\paragraph{Student's $t$ CI}
The procedure for constructing a Student's $t$ CI based on standard bootstrap is
described in \citet{efron1993introduction}. \jy{give page or section number when
  citing a book}
With block bootstrapping, a $(1 - \alpha)$ Student's $t$ CI is
\[
(\hat{\theta}_{n} - t_{(1-\alpha/2), k - 1}\hat{\text{SE}}, \quad
\hat{\theta}_{n} - t_{(\alpha/2), k -1}\hat{\text{SE}}),
\]
where $k$ is the number of blocks.
This CI is centered by the point estimator $\hat\theta_n$ and is symmetric.
Like the standard 
normal interval, the Student's $t$ CI is a table-based bootstrap interval
approach. In this case,
its validity relies on whether the distribution of $\hat\theta_n$ is
reasonably well approximation by the $t_{k-1}$ distribution with an
expected value of $\theta$, and whether the bootstrap 
$\widehat{\text{SE}}$ approximates the true standard error.

\paragraph{Percentile CI}
The percentile CI was first suggested in \citet{efron1979bootstrap}.
Let $\hat\theta_{n, \alpha}^{(b)}$ be the empirical $100\alpha$th percentile of
$\{\hat\theta_n^{(1)}, \ldots, \hat\theta_n^{(B)}\}$. The $(1 - \alpha)$
empirical percentile CI is
\[
(\hat\theta_{n, \alpha/2}^{(b)}, \quad \hat\theta_{n, 1 - \alpha/2}^{(b)}).
\]
This CI is not necessarily centered by the point estimator $\hat\theta_n$.
As will be shown in our simulation study, this approach works well for the
marginal mean and standard deviation of a serially dependent process, but its
coverage of the temporal dependence deteriorates as $n$ increases, which is
contrary to what one would expect.

@@

\paragraph{Bias Corrected Bootstrap CI}
The procedure for constructing a Bias Corrected Bootstrap CI based on standard
bootstrap is
described in \citet{carpenter2000bootstrap}.
Let $b = \Phi^{-1}\{\#\{\hat\theta_n^{(b)} < \hat{\theta}_n\} / B\}$
for $b \in \{1, \ldots, B\}$. 
For a $1 - \alpha$ CI, let
\[
\alpha_1 = \Phi(2b - z_{\alpha/2}).
\]
\[
\alpha_2 = \Phi(2b - z_{1 - \alpha/2}).
\]
A $(1 - \alpha) BC_a$ CI is
\[
(\hat\theta_{n, \alpha_1}^{(b)}, \quad \hat\theta_{n, \alpha_2}^{(b)}).
\]

\paragraph{Bias Corrected and Accelerated ($BC_a$) Bootstrap CI}
The $BC_a$ CI was first suggested in \citet{efron1987better}.
\eds{a different abbrevation/notation was used for this in the introduction}
\mc{used $BC_a$}
\jy{Isn't this just the empirical CDF? We just need the sample quantile functon.
  What is your reference for this description?}
Let $\hat{z}_0 = \Phi^{-1}\{\#\{\hat\theta_n^{(b)} < \hat{\theta}_n\} / B\}$
for $b \in \{1, \ldots, B\}$. 
Let $Z_{(i)}$ be the original sample without the $i$th block $z_i$, let
$\hat{\theta}_{(i)}$ be the jackknife values of $Z_{(i)}$
for $i \in \{1, \ldots, n\}$, 
and let $\hat{\theta}_{(.)} = \sum_{i=1}^{k} \hat{\theta}_{(i)} / k$. 
Let 
\[
\hat{a} = \frac{\sum_{i=1}^{k} (\hat{\theta}_{(.)} -
  \hat{\theta}_{(i)})^3}{6\{\sum_{i=1}^{k} (\hat{\theta}_{(.)} -
  \hat{\theta}_{(i)})^2\}^{3/2}}
.\] For a $1 - \alpha$ CI, let
\[
\alpha_1 = \Phi(z_0 + \frac{z_{0} +
  z_{\alpha/2}}{1 - \hat{a}(z_{0} + z_{\alpha/2})}).
\]
\[
\alpha_2 = \Phi(z_0 + \frac{z_{0} +
  z_{1 - \alpha/2}}{1 - \hat{a}(z_{0} + z_{1 - \alpha/2})}).
\]
\eds{notation will need to be cleaned and clarified}
A $(1 - \alpha) BC_a$ CI is
\[
(\hat\theta_{n, \alpha_1}^{(b)}, \quad \hat\theta_{n, \alpha_2}^{(b)}).
\]
This CI is not necessarily centered by the point estimator $\hat\theta_n$. The
$BC_a$ method corrects for bias and skewness of the $B$ bootstrap point
estimates $\{\hat\theta_n^{(1)}, \ldots, \hat\theta_n^{(B)}\}$ by including
bias-correction and acceleration factors. The acceleration factor refers to
the 
rate of change of of the standard error of $\hat\theta_n$ with respect to
$\theta$.

\paragraph{Proposed Method CI}
Our Proposed Method CI is centered at the point estimator and uses the
variation
in the bootstrap estimates to construct the error bound. This interval requires
the computation of $\bar\theta_n^{(b)}$, the mean of all bootstrap point
estimates, and $\widehat{\text{bias}} = \bar\theta_n^{(b)} - \hat\theta_n$.
A $(1 - \alpha)$ CI using our Proposed Method is
\[
(\hat\theta_{n, \alpha/2}^{(b)} - \widehat{\text{bias}}, \quad
\hat\theta_{n, 1 - \alpha/2}^{(b)} - \widehat{\text{bias}}).
\]
This CI is necessarily centered around .... and
is asymmetric, as different critical values are used to compute
the lower and upper bounds.

@@

Three target parameters of $X_t$ were considered:
1) $\mu = 0$, the mean of $X_t$;
2) $\sigma_x = 1$, the standard deviation of $X_t$; and
2) $\phi$, the lag-1 auto-correlation coefficient.
To investigate the effect of sample size~$n$, we considered an array of values
$n \in \{100, 200, 400, 800, 1600, 3200\}$. In each configuration, we generated 10000
replicates. For each replicate, we constructed three 95\% block bootstrap
CIs for each parameter as described in the last section. We can estimate 
$\mu$, $\sigma_x$, and $\phi$ by computing the sample mean, sample 
standard deviation,
and lag-1 auto-correlation, respectively, of each bootstrap sample, and then 
constructing intervals for each parameter using the appropriate procedures
described in Section~\ref{sec:bbci} .
Then we estimated their actual coverage rates along with their 95\% confidence
intervals from the 10000 replicates. The block bootstrap sampling step was done
with function \texttt{tsboot} from R package \textsl{boot} \citep{boot}, with
block size $\lceil n / l \rceil$. This function by default is an implementation
of moving block bootstrap as described in the previous section, meaning that
that blocks are allowed to wrap around, and $l = \lceil n^{1/3} \rceil$.

\eds{Is $l = \lceil n^{1/3} \rceil$? Is it also worth investigating different 
choices of $l$ for fixed (large) $n$?}
\mc{Addressed in the Block Bootstrap Sample subsection}
\eds{how did you estimate $\mu$, $\sigma_x$ and $\phi$?}
\mc{addressed}

@@

\jy{Make it flow better and conciser}
The coverage rates of the CIs were used to compare the performance of CIs. Let
$\hat\theta_{L, r}$ and $\hat\theta_{U, r}$ be the lower and upper bound,
respectively, for the confidence interval constructed for each replicate
$r \in \{1, \ldots, R\}$, where $R$ is the
number of replicates.
Then $cov = \#\{\hat\theta_{L, r} < \theta < \hat\theta_{U, r} \}/R$,  
for $r \in \{1, \ldots, R\}$.
\eds{this notation is a bit sloppy, as it implies $n_{CI}$ changes for each 
value of $CI$; consider using a summation of indicators with a different index}
\mc{replaced $CI$ with $r$, and $n_{CI}$ with $R$}
If a CI method is valid, then the coverage rate is expected to match the
nominal 
level. Because it is unlikely for the coverage to exactly match the nominal
level,
we can construct a 95\% CI of the coverage
rate (which is an estimate of a proportion with $n = 10000$). If the proportion
0.95 is included in the interval, the block bootstrap method is likely
performing
well. If all values in the interval are below 0.95, the results would suggest 
that the
method either is providing inaccurate estimation, is underestimating the
process' variability, or a combination of both. If all values in the interval
are above .95, the results suggest that the method is overestimating the
process' variability.

@@

\begin{figure}[tbp]
  \centering
  \includegraphics[width=\textwidth]{figures/plot_sigma}
  \caption{Empirical coverage rates of different 95\% block bootstrap CIs for
    the marginal standard deviation $\sigma$ of an AR(1) process with AR
    coefficient $\phi \in \{-0.4, 0.2, 0, 0.2, 0.4\}$ and series length
    $n \in \{100, 200, 400, 800, 1600, 3200\}$ based on 10,000 replicates.
    The error bars represent 95\% CIs of the real coverage rates.}
  \label{fig:sigma}
\end{figure}

@@

Based on Figure~\ref{fig:mu}, 
Student's $t$ CIs appear to have the greatest coverage rates with respect 
to estimating $\mu$. In fact, for $\phi = -0.4$, Student's $t$ CIs over-cover $\mu$
for all sample sizes, whereas other CIs have coverage rates that
hover around the $95\%$ line at this level of $\phi$. For $\phi \geq -0.2$,
$BC_a$ CIs undercover $\mu$ for all $n$ observed. For $\phi = -0.2$, 
Standard, Percentile, %CBP, 
Proposed Method, and $BC$ CIs seem to 
generally cover $\mu$ at the nominal 
rate when $n \geq 400$. Student's $t$ CIs either recover or over-cover $\mu$
for $n \geq 100$. For $\phi = 0$, or when the 
sample is independently normally distributed, $n = 1600$ seems to 
be enough to recover $\mu$ when using Standard, Percentile, 
%CBP, 
Proposed Method, or $BC$ 
CIs. Student's $t$ CIs cover $\mu$ at the nominal rate for $n \geq 100$ at 
$\phi = 0$.
For $\phi = 0.2$, $n > 3200$ seems to be necessary to recover $\mu$
at the nominal level when using
any of the CIs, although some CIs, such as Student's $t$, are much closer to the
$95\%$ line than others, most notably $BC_a$.
For $\phi = 0.4$, a much larger sample size appears to be necessary. Once again,
Student's $t$ CIs are the closest to $95\%$ coverage, and $BC_a$ CIs are the furthest.

Based on Figure~\ref{fig:sigma}, 
$BC_a$ CIs greatly undercover $\sigma_x$ for every combination of $n$ and 
$\phi$, observed, although
there is no trend of coverage deterioration, indicating that there may eventually
be a sample size large enough for $\sigma_x$ to be covered at the nominal level.
For $\phi = -0.4$, Standard Normal and Student's $t$ CIs recover $\sigma$ when 
$n = 1600$, but undercover $\sigma$ for $n = 3200$, indicating
that a larger $n$ is most likely necessary to consistently cover $\sigma$ at the 
nominal rate.
The other CI types undercover $\sigma$ for all sample sizes at $\phi = 0.4$.
For $\phi  = -0.2$, all CIs except for $BC_a$ are able to cover $\sigma$ at the 
nominal rate for $n \geq 3200$, and Student's $t$ CIs cover $\sigma$ at the 
nominal rate when $n \geq 400$. When $\phi = 0$, $n \geq 1600$ seems to 
be large enough if Standard CIs are used, and $n \geq 400$ is fine is
Student's $t$ CIs are used. $n \geq 3200$ appears necessary 
for other CIs. For $\phi = 0.2$, 
comfortable coverage of $\sigma$ at the nominal level appears to only be true
for Student's $t$ CIs for $n \geq 3200$, although Standard %and CBP% 
CIs do reach the nominal level in our simulation results. For $\phi = 0.4$, a much
larger sample size appears to be necessary. Student's $t$ CIs are the closest to
$95\%$ coverage, and $BC_a$ CIs are the furthest.

Based on Figure~\ref{fig:phi}, 
Percentile, %CBP, %
$BC$, and $BC_a$ CIs deteriorate clearly for any level of temporal correlation,
so they should not be used. The deterioration becomes more evident
as the absolute value of $\phi$ increases, regardless of whether $\phi$ is 
negative or positive. When $\phi = -0.4$, Standard and Proposed Method CIs 
recover $\phi$ at the nominal rate for $n \geq 400$. At this $\phi$ level,
Student's $t$ CIs either recover or over-cover $\phi$ for $n \geq 100$. When
$\phi = -0.2$, Standard and Proposed Method CIs recover $\phi$ at $n = 800$ and 
$n = 1600$, 
although they undercover $\phi$ at $n = 3200$, indicating that 
perhaps a larger $n$ is needed if these CIs are uses. However,
Student's $t$ CIs cover $\phi$ at the nominal level for $n \geq 400$. When
$\phi = 0$, Standard and Proposed Method CIs recover $\phi$ relatively comfortably 
at $n = 3200$, and 
$n = 800$ seems to be sufficient for Student's $t$ CIs. For $\phi = 0.2$, Standard
and Proposed Method CIs cover $\phi$ at the nominal rate for $n \geq 1600$, whereas 
Student's $t$ CIs can accomplish this at $n \geq 100$. For $\phi = 0.4$, $n \geq 
800$ is large enough for Standard and Proposed Method CIs. Student's $t$ CIs either
recover or over-cover $\phi$ for all $n \geq 100$.

To summarize, the CI type chosen should be based on the target parameter. 
When estimating $\mu$, the Student's $t$ CI seems to have the highest coverage
overall, although that leads to over-coverage when $\phi$ is -0.4. For a
sample with no temporal dependence, the Student's $t$ CI cover $\mu$ perfectly
at the nominal rate even for small sample sizes. For positive $\phi$, a larger
sample size appears to be necessary regardless of the CI used. In the case
that $\phi$ is unknown and expected to be greater than $0$, $n > 3200$ may be
necessary for block bootstrap interval estimation of $\mu$. If $\phi$ is known,
a lesser sample size may be sufficient. When estimating $\sigma$,
$BC_a$ should not be used, and Student's $t$ again has the greatest coverage
rates. In the case that $\phi$ is unknown and expected to be greater than $0$,
$n > 3200$ may be necessary for block bootstrap interval estimation of
$\sigma$. Again, if $\phi$ is known, a lesser sample size may be enough.
When estimating $\phi$, Percentile and $BC_a$ CIs 
deteriorate in coverage, indicating they should not be used in this context. 
Increasing $n$ will not fix the performance of either of these intervals 
because the assumption that the coverage rate will approach the nominal level
as $n$ increases is invalid. Standard and Proposed Method CIs managed to fix the
deterioration problem, and they perform similarly, but Student's $t$ covers
$\phi$ at the nominal rate for much smaller sample sizes. It seems that 
$n = 800$ is large enough to
recover $\phi$ when using the Student's $t$ method.

@@

As shown in Figure~\ref{fig:phi}, Percentile CIs appear to suffer from bias;
specifically, they seem to heavily underestimate $\phi$. As shown in
Figure~\ref{fig:bc}, $BC$ CIs do seem to correct this bias on average, but the width of
  the 
CIs is very inconsistent. From Figure~\ref{fig:prop}, we can see that 
  $prop$ CIs correct the bias using $\widehat{\text{bias}} = \bar\theta_n^{(b)} -
  \hat\theta_n$, which seems to usually be negative, indicating a positive correction
  from
interval construction in \ref{sec:bbci}.

>>>>

The necessary sample size for bootstrap standard errors to provide valid
uncertainty measures in practice has not been extensively studied. For
independent data and non-block bootstrap, \citet{hesterberg2015teachers} notes
that while percentile-based CIs \eds{for the mean? differences in means?} from 
nonparametric bootstrap
are more accurate than $t$-intervals for larger sample sizes, they are
less accurate for smaller sample sizes. \citet{chernick2009revisiting} finds 
that the best choice of method for estimating
the parameter of a distribution is dependent on the sample size, the number of
bootstrap resamples, and the confidence level. In the context of structural equation
modeling, \citet{nevitt2001performance} find
that a sample size of 200--1000 is usually sufficient for interval estimation
using standard nonparametric bootstrap. For dependent data, the necessary
sample
size for bootstrap is even less clear. In the setting of linear regression with a
focus on estimating the proportion of 
variation attributable to a certain variable, \citet{burch2012nonparametric} finds
that three nonparametric bootstrap methods (Standard, Percentile, and Bias-Corrected
and
Accelerated) approach the coverage of a pivotal quantity as $n$ gets larger for an
underlying normal distribution. However, they find that for other distributions, 
coverage may deteriorate as $n$ increases. 
When attempting to create interval estimations for the Pearson correlation 
coefficient of bivariate normal data, \citet{puth2015variety} find bootstrap 
methods to be less accurate than the Fisher's transformation method even 
for a sample of size $n = 100$ and correlation coefficient equivalent to 0.
Few studies have provided a practical guide on what size is needed
for block bootstrap inference for dependent data.
In a linear regression setting
with
dependent data where the
regression errors are generated from a homoscedastic AR(1) process, 
\citet{goncalves2005bootstrap} find that standard error
estimates from moving 
block bootstrap in small samples may be more accurate than
inference from closed-form asymptotic estimates, but moving block bootstrap 
\jy{did they do block or standard bootstrap?}
\mc{moving block bootstrap}
CIs still do not have sufficient coverage of the target parameter even for sample size
$n = 1024$.
\jy{I added more references to the reference folder that studied coverage of
  bootstrap CIs but not block bootstrap CIs.}

@@

\paragraph{Standard Normal CI}
Assuming that $\hat\theta_n$ is asymptotically normally distributed with
$\theta$ as the mean, we just need an estimate of the standard error to
construct an approximate CI \citep[p.168]{efron1993introduction}.
Let $\widehat{\text{SE}}$ be the empirical standard error of the block bootstrap
copies of $\hat\theta_n^{(b)}$, $b = 1, \ldots, B$.
A $(1 - \alpha)100\%$ standard normal CI is
\[
(\hat{\theta}_{n} - z_{(1-\alpha/2)}\widehat{\text{SE}}, \quad
\hat{\theta}_{n} - z_{(\alpha/2)}\widehat{\text{SE}}).
\]
\eds{define $z_{(.)}$ and check the signs}
This CI is centered by the point estimator $\hat\theta_n$ and is symmetric.
Its validity relies on whether the distribution of $\hat\theta_n$ is reasonably
well approximated by its asymptotic normal distribution and whether the
bootstrap $\widehat{\text{SE}}$ approximates the true standard error.

\paragraph{Student's $t$ CI}
The procedure for constructing a Student's $t$ CI based on standard bootstrap is
described in \citet{efron1993introduction}. \jy{give page or section number when
  citing a book}
With block bootstrapping, a $(1 - \alpha)100\%$ Student's $t$ CI is
\[
(\hat{\theta}_{n} - t_{(1-\alpha/2), k - 1}\hat{\text{SE}}, \quad
\hat{\theta}_{n} - t_{(\alpha/2), k -1}\hat{\text{SE}}),
\]
\eds{define $t_{(.)}$ and check the signs}
where $k$ is the number of blocks.
This CI is centered by the point estimator $\hat\theta_n$ and is symmetric.
Like the standard 
normal interval, the Student's $t$ CI is a table-based bootstrap interval
approach. In this case,
its validity relies on whether the distribution of $\hat\theta_n$ is
reasonably well approximation by the $t_{k-1}$ distribution with an
expected value of $\theta$, and whether the bootstrap 
$\widehat{\text{SE}}$ approximates the true standard error.

\paragraph{Percentile CI}
The percentile CI was first suggested in \citet{efron1979bootstrap}.
Let $\hat\theta_{n, \alpha}^{(b)}$ be the empirical $100\alpha$th percentile of
$\{\hat\theta_n^{(1)}, \ldots, \hat\theta_n^{(B)}\}$. The $(1 - \alpha)100\%$
empirical percentile CI is
\[
(\hat\theta_{n, \alpha/2}^{(b)}, \quad \hat\theta_{n, 1 - \alpha/2}^{(b)}).
\]
This CI is not necessarily centered by the point estimator $\hat\theta_n$.
As will be shown in our simulation study, this approach works well for the
marginal mean and standard deviation of a serially dependent process, but its
coverage of the temporal dependence deteriorates as $n$ increases, which is
contrary to what one would expect.

@@

\paragraph{Bias Corrected ($BC$) Bootstrap CI}
The procedure for constructing a Bias Corrected Bootstrap CI based on standard
bootstrap is
described in \citet{carpenter2000bootstrap}.
Let $b = \Phi^{-1}\{\#\{\hat\theta_n^{(b)} < \hat{\theta}_n\} / B\}$
for $b \in \{1, \ldots, B\}$. 
For a $(1 - \alpha)100\%$ CI, let
\[
\alpha_1 = \Phi(2b - z_{\alpha/2}).
\]
\[
\alpha_2 = \Phi(2b - z_{1 - \alpha/2}).
\]
A $(1 - \alpha)100\%~BC$ CI is
\[
(\hat\theta_{n, \alpha_1}^{(b)}, \quad \hat\theta_{n, \alpha_2}^{(b)}).
\]

\paragraph{Bias Corrected and Accelerated ($BC_a$) Bootstrap CI}
The $BC_a$ CI was first suggested in \citet{efron1987better}.
\jy{Isn't this just the empirical CDF? We just need the sample quantile functon.
  What is your reference for this description?}
Let $\hat{z}_0 = \Phi^{-1}\{\#\{\hat\theta_n^{(b)} < \hat{\theta}_n\} / B\}$
for $b \in \{1, \ldots, B\}$. 
Let $Z_{(i)}$ be the original sample without the $i$th block $z_i$, let
$\hat{\theta}_{(i)}$ be the jackknife values of $Z_{(i)}$
for $i \in \{1, \ldots, n\}$, 
and let $\hat{\theta}_{(.)} = \sum_{i=1}^{k} \hat{\theta}_{(i)} / k$. 
Let 
\[
\hat{a} = \frac{\sum_{i=1}^{k} (\hat{\theta}_{(.)} -
  \hat{\theta}_{(i)})^3}{6\{\sum_{i=1}^{k} (\hat{\theta}_{(.)} -
  \hat{\theta}_{(i)})^2\}^{3/2}}
.\] For a $(1 - \alpha)100\%$ CI, let
\[
\alpha_1 = \Phi\left(z_0 + \frac{z_{0} +
  z_{\alpha/2}}{1 - \hat{a}(z_{0} + z_{\alpha/2})}\right).
\]
\[
\alpha_2 = \Phi\left(z_0 + \frac{z_{0} +
  z_{1 - \alpha/2}}{1 - \hat{a}(z_{0} + z_{1 - \alpha/2})}\right).
\]
A $(1 - \alpha)100\%~BC_a$ CI is
\[
(\hat\theta_{n, \alpha_1}^{(b)}, \quad \hat\theta_{n, \alpha_2}^{(b)}).
\]
This CI is not necessarily centered by the point estimator $\hat\theta_n$. The
$BC_a$ method corrects for bias and skewness of the $B$ bootstrap point
estimates $\{\hat\theta_n^{(1)}, \ldots, \hat\theta_n^{(B)}\}$ by including
bias-correction and acceleration factors. The acceleration factor refers to
the 
rate of change of of the standard error of $\hat\theta_n$ with respect to
$\theta$.

\paragraph{Proposed Method CI}
Our Proposed Method CI is centered at the point estimator and uses the
variation
in the bootstrap estimates to construct the error bound. This interval requires
the computation of $\bar\theta_n^{(b)}$, the mean of all bootstrap point
estimates, and $\widehat{\text{bias}} = \bar\theta_n^{(b)} - \hat\theta_n$.
A $(1 - \alpha)100\%$ CI using our Proposed Method is
\[
(\hat\theta_{n, \alpha/2}^{(b)} - \widehat{\text{bias}}, \quad
\hat\theta_{n, 1 - \alpha/2}^{(b)} - \widehat{\text{bias}}).
\]
This CI is necessarily centered around .... and
is asymmetric, as different critical values are used to compute
the lower and upper bounds.

@@

Three target parameters of $X_t$ were considered:
1) $\mu = 0$, the mean of $X_t$;
2) $\sigma_x = 1$, the standard deviation of $X_t$; and
2) $\phi$, the lag-1 auto-correlation coefficient.
To investigate the effect of sample size~$n$, we considered an array of values
$n \in \{100, 200, 400, 800, 1600, 3200\}$. In each configuration, we generated 
10000 replicates. For each replicate, we constructed seven 95\% block bootstrap
CIs for each parameter as described in the last section. We can estimate 
$\mu$, $\sigma_x$, and $\phi$ by computing the sample mean, sample 
standard deviation,
and lag-1 auto-correlation, respectively, of each bootstrap sample, and then 
construct intervals for each parameter using the appropriate procedures
described in Section~\ref{sec:bbci}.
Then we estimated their actual coverage rates along with their 95\% confidence
intervals from the 10000 replicates. The block bootstrap sampling step was done
with function \texttt{tsboot} from R package \textsl{boot} \citep{boot}, with
block size $\lceil n / l \rceil$. This function by default is an implementation
of moving block bootstrap as described in the previous section, meaning that
that blocks are allowed to wrap around, and $l = \lceil n^{1/3} \rceil$.

@@

\jy{Make it flow better and conciser}
The coverage rates of the CIs were used to compare the performance of CIs. Let
$\hat\theta_{L, r}$ and $\hat\theta_{U, r}$ be the lower and upper bound,
respectively, for the confidence interval constructed for each replicate
$r \in \{1, \ldots, R\}$, where $R$ is the
number of replicates.
Then $cov = \#\{\hat\theta_{L, r} < \theta < \hat\theta_{U, r} \}/R$,  
for $r \in \{1, \ldots, R\}$.
If a CI method is valid, then the coverage rate is expected to match the
nominal 
level. Because it is unlikely for the coverage to exactly match the nominal
level,
we can construct a 95\% CI of the coverage
rate (which is an estimate of a proportion with $n = 10000$ \eds{R?}). If the
proportion
0.95 is included in the interval, the block bootstrap method is likely
performing
well. If all values in the interval are below 0.95, the results would suggest 
that the
method either is providing inaccurate estimation, is underestimating the
process' variability, or a combination of both. If all values in the interval
are above .95, the results suggest that the method is overestimating the
process' variability.

@@

\begin{figure}[tbp]
  \centering
  \includegraphics[width=\textwidth]{figures/plot_sigma}
  \caption{Empirical coverage rates of different 95\% block bootstrap CIs for
    the marginal standard deviation $\sigma_x$ of an AR(1) 
		process with AR
    coefficient $\phi \in \{-0.4, 0.2, 0, 0.2, 0.4\}$ and series length
    $n \in \{100, 200, 400, 800, 1600, 3200\}$ based on 10,000 replicates.
    The error bars represent 95\% CIs of the real coverage rates.}
  \label{fig:sigma}
\end{figure}

@@

Based on Figure~\ref{fig:mu}, 
Student's $t$ CIs appear to have the greatest \eds{largest?} coverage rates with 
respect 
to estimating $\mu$. In fact, for $\phi = -0.4$, Student's $t$ CIs over-cover 
$\mu$ for all sample sizes, whereas other CIs have coverage rates that
hover around the $95\%$ line at this level of $\phi$. For $\phi \geq -0.2$,
$BC_a$ CIs undercover $\mu$ for all $n$ observed. For $\phi = -0.2$, 
Standard, Percentile, %CBP, 
Proposed Method, and $BC$ CIs seem to 
generally cover $\mu$ at the nominal 
rate when $n \geq 400$. Student's $t$ CIs either recover or over-cover $\mu$
for $n \geq 100$. For $\phi = 0$, or when the 
sample is independently normally distributed, $n = 1600$ seems to 
be enough to recover $\mu$ when using Standard, Percentile, 
%CBP, 
Proposed Method, or $BC$ 
CIs. Student's $t$ CIs cover $\mu$ at the nominal rate for $n \geq 100$ at 
$\phi = 0$.
For $\phi = 0.2$, $n > 3200$ seems to be necessary to recover $\mu$
at the nominal level when using
any of the CIs, although some CIs, such as Student's $t$, are much closer to the
$95\%$ line than others, most notably $BC_a$.
For $\phi = 0.4$, a much larger sample size appears to be necessary. Once again,
Student's $t$ CIs are the closest to $95\%$ coverage, and $BC_a$ CIs are the 
furthest.

Based on Figure~\ref{fig:sigma}, 
$BC_a$ CIs greatly undercover $\sigma_x$ for every combination of $n$ and 
$\phi$ observed, although there is no trend of coverage deterioration, 
indicating that there may eventually
be a sample size large enough for $\sigma_x$ to be covered at the nominal level.
For $\phi = -0.4$, Standard Normal and Student's $t$ CIs recover $\sigma_x$ when 
$n = 1600$, but undercover $\sigma_x$ for $n = 3200$, indicating
that a larger $n$ is most likely necessary to consistently cover $\sigma_x$ at 
the nominal rate.
The other CI types undercover $\sigma_x$ for all sample sizes at $\phi = 0.4$.
For $\phi  = -0.2$, all CIs except for $BC_a$ are able to cover $\sigma_x$ at 
the nominal rate for $n \geq 3200$, and Student's $t$ CIs cover $\sigma$ at the 
nominal rate when $n \geq 400$. When $\phi = 0$, $n \geq 1600$ seems to 
be large enough if Standard CIs are used, and $n \geq 400$ is fine is
Student's $t$ CIs are used. $n \geq 3200$ appears necessary 
for other CIs. For $\phi = 0.2$, 
comfortable coverage of $\sigma_x$ at the nominal level appears to only be true
for Student's $t$ CIs for $n \geq 3200$, although Standard %and CBP% 
CIs do reach the nominal level in our simulation results. For $\phi = 0.4$, a much
larger sample size appears to be necessary. Student's $t$ CIs are the closest to
$95\%$ coverage, and $BC_a$ CIs are the furthest.

Based on Figure~\ref{fig:phi}, 
Percentile, %CBP, %
$BC$, and $BC_a$ CIs deteriorate clearly for any level of temporal correlation,
so they should not be used. The deterioration becomes more evident
as the absolute value of $\phi$ increases, regardless of whether $\phi$ is 
negative or positive. When $\phi = -0.4$, Standard and Proposed Method CIs 
recover $\phi$ at the nominal rate for $n \geq 400$. At this $\phi$ level,
Student's $t$ CIs either recover or over-cover $\phi$ for $n \geq 100$. When
$\phi = -0.2$, Standard and Proposed Method CIs recover $\phi$ at $n = 800$ and 
$n = 1600$, 
although they undercover $\phi$ at $n = 3200$, indicating that 
perhaps a larger $n$ is needed if these CIs are used. However,
Student's $t$ CIs cover $\phi$ at the nominal level for $n \geq 400$. When
$\phi = 0$, Standard and Proposed Method CIs recover $\phi$ relatively 
comfortably at $n = 3200$, and 
$n = 800$ seems to be sufficient for Student's $t$ CIs. For $\phi = 0.2$, Standard
and Proposed Method CIs cover $\phi$ at the nominal rate for $n \geq 1600$, whereas 
Student's $t$ CIs can accomplish this at $n \geq 100$. For $\phi = 0.4$, $n \geq 
800$ is large enough for Standard and Proposed Method CIs. Student's $t$ CIs either
recover or over-cover $\phi$ for all $n \geq 100$.

To summarize, the CI type chosen should be based on the target parameter. 
When estimating $\mu$, the Student's $t$ CI seems to have the highest coverage
overall, although that leads to over-coverage when $\phi$ is -0.4. For a
sample with no temporal dependence, the Student's $t$ CI cover $\mu$ perfectly
at the nominal rate even for small sample sizes. For positive $\phi$, a larger
sample size appears to be necessary regardless of the CI used. In the case
that $\phi$ is unknown and expected to be greater than $0$, $n > 3200$ may be
necessary for block bootstrap interval estimation of $\mu$. If $\phi$ is known,
a lesser sample size may be sufficient. When estimating $\sigma_x$,
$BC_a$ should not be used, and Student's $t$ again has the greatest 
\eds{highest?} coverage
rates. In the case that $\phi$ is unknown and expected to be greater than $0$,
$n > 3200$ may be necessary for block bootstrap interval estimation of
$\sigma_x$. Again, if $\phi$ is known, a lesser sample size may be enough.
When estimating $\phi$, Percentile and $BC_a$ CIs 
deteriorate in coverage, indicating they should not be used in this context. 
Increasing $n$ will not fix the performance of either of these intervals 
because the assumption that the coverage rate will approach the nominal level
as $n$ increases is invalid. Standard and Proposed Method CIs managed to fix the
deterioration problem, and they perform similarly, but Student's $t$ covers
$\phi$ at the nominal rate for much smaller sample sizes. It seems that 
$n = 800$ is large enough to
recover $\phi$ when using the Student's $t$ method.

@@

As shown in Figure~\ref{fig:phi}, Percentile CIs appear to suffer from bias;
specifically, they seem to heavily underestimate $\phi$. As shown in
Figure~\ref{fig:bc}, $BC$ CIs do seem to correct this bias on average, but the width of
  the 
CIs is very inconsistent. From Figure~\ref{fig:prop}, we can see that the 
Proposed Method CIs correct the bias using 
$\widehat{\text{bias}} = \bar\theta_n^{(b)} -
  \hat\theta_n$, which seems to usually be negative, indicating a positive 
	correction from interval construction in Section~\ref{sec:bbci}.
